\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}

\title{Orbit: A Framework for Symbiotic Homeostasis in Sovereign Agentic Infrastructures}

\author{
  Symbeon Labs \\
  Advanced Agentic Engineering Department \\
  \texttt{research@symbeon.io} \\
}

\date{January 2026}

\begin{document}

\maketitle

\begin{abstract}
As autonomous agents and Large Language Models (LLMs) transition from isolated interfaces to integrated infrastructure operators, the friction between high-level intelligence and low-level system entropy becomes a critical bottleneck. This paper introduces \textbf{Orbit-DevOps}, an algebraic reasoning engine and multi-platform command center designed to maintain system homeostasis. We formalize the \textit{Mathematica Orbitae} framework, a non-semantic approach to system vitality based on the interplay between Entropy ($\Omega$), Resource Vitality ($\Phi$), and Agent Symbiosis ($\Sigma$). Our results demonstrate a significant reduction in contextual debt and a stabilization of agentic environments across Windows, Linux, and macOS platforms.
\end{abstract}

\textbf{Keywords:} Agentic Infrastructure, Symbiotic Computing, Homeostasis, Entropy Reduction, Autonomous Systems, Mathematica Orbitae.

\section{Introduction}
The paradigm of "Agent-Centric Infrastructure" requires a shift from passive maintenance to active, symbiotic management. Traditional DevOps tools prioritize human-readable configurations and manual triggers. In contrast, autonomous agents require environments that are predictable, self-healing, and context-aware. Orbit was developed as the "Sovereign Backbone" for these entities, providing a unified control layer that treats system resources as biological variables subject to homeostatic regulation.

\section{Mathematica Orbitae: The Formal Logic}
The core of Orbit is the algebraic representation of system health. We define the state vector $s \in \mathbb{R}^3_+$ as:
\begin{equation}
s = \begin{bmatrix} \Omega \\ \Phi \\ \Sigma \end{bmatrix}
\end{equation}

Where:
\begin{itemize}
    \item $\Omega$ (Entropy): $[0, 1]$ - Measure of system noise, residual data, and ghost processes.
    \item $\Phi$ (Vitality): $[0, 1]$ - Normalized availability of raw resources (CPU, RAM, Disk).
    \item $\Sigma$ (Symbiosis): $[0, 1]$ - Alignment between the Agent DNA and host infrastructure.
\end{itemize}

\subsection{The Vitality Equation}
The Agentic Vitality Index ($V_a$) is calculated as follows:
\begin{equation}
V_a = \left( \frac{\Phi}{\Omega + 1} \right) \cdot \Sigma^e
\end{equation}
Where $e$ is the efficiency coefficient of the provisioned stack. This equation proves that resource availability alone is insufficient; minus alignment ($\Sigma$) or excessive noise ($\Omega$), the agent's contextual coherence collapses.

\section{Universal Provider Architecture}
To ensure sovereignty, Orbit-DevOps employs a decoupled provider pattern. The \textit{BaseProvider} interface abstracts platform-specific complexities, allowing the \textit{Algebraic Core} to operate identically on Windows (via PowerShell-driven \textit{WindowsProvider}) and Unix-like systems (via POSIX-compliant \textit{UnixProvider}).

\section{Sovereignty and Protection}
Intellectual property and system integrity are guarded through the \textit{Symbeon Zero Protocol}. This framework employs "Strategic Ambiguity" in public-facing concludes while maintaining a proprietary reasoning engine. This ensures that the precise gradients of optimization remain a sovereign asset, preventing obsolescence and unauthorized replication of the homeostatic logic.

\section{Conclusion}
Orbit-DevOps v1.4.1 formalizes the transition from artisanal script management to an "Agentic Operating System." By grounding infrastructure in the rigorous logic of the \textit{Mathematica Orbitae}, we provide the stability required for the flourishing of autonomous intelligence in the coming era of symbiotic computing.

\section*{References}
\begin{thebibliography}{99}
\bibitem{symbeon2026} Symbeon Labs, "The Sovereign Symbiote: A Manifesto for Agentic Infrastructure," \textit{Internal Research Repository}, 2026.
\bibitem{orbitmath} Orbit-DevOps Technical Documentation, "Mathematica Orbitae Fundamentals," \textit{v1.4.1}, 2026.
\end{thebibliography}

\end{document}
